---
title: "SPRM_Project"
author: "Matt Hirschi"
date: "November 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mosaic)
library(car)
library(janitor)
dat <- read_csv("basketball2.csv")
dat <- clean_names(dat)
dat$person <- as.factor(dat$person)
dat$type <- as.factor(dat$type)
dat$x_u_feff_distance <- as.factor(dat$x_u_feff_distance)
```

## Question

Does the distance and type of shot effect how many baskets they make? 

Null: freethrow = threepointer
Alternative: freethrow not equal to threepointer

Null: p1=p2=p3=p4=p5=p6=p7=p8
Alternative: At least one is different

Null: underhand = regular
Alternative: not equal to eachother


I assigned each shooter a number between 1-8 and then used a random number generator to choose the order they shot and which shot they used as well what distance they shot from. 

The factors were the distance they shot from, the person, and the type of shot they shot. The response was how many shots they made. 

## Numerical Descriptive Statistics

```{r}
favstats(dat$made ~ dat$x_u_feff_distance)
favstats(dat$made ~ dat$person)
favstats(dat$made ~ dat$type)
```


## Descriptive Graphics

```{r}
dat %>%
  ggplot(aes(x = person, y = made))+
  geom_boxplot()

dat %>% 
  ggplot(aes(x = type, y = made))+
  geom_boxplot()
```

## Inferential Statistics 

Based on the p-value nothing is significant and we accept all the null hypothesis' that everything is equal and we find no significance within the factors or the blockings. 
```{r}
model <- aov(made ~ x_u_feff_distance + person + type + x_u_feff_distance:person, data = dat)

model1 <- aov(made ~ x_u_feff_distance + Error(person) + type + x_u_feff_distance:person,
             data = dat)

summary(model1)

plot(model, which = 1:2)
```


## Conclusion

I think I got the results I did because everyone was quite good at basketball and were on their game this day. I would have found random people to do this experiment instead of people I knew and their skill level. 